---
title: "ScrapeBase2013"
output: html_document
---

```{r}
library(rvest)
library(tidyverse)
library(RSelenium)
library(XML)
library(data.table)
library(sendmailR)
```

## Open the csv file
```{r}
rawData_2013 <- fread('/Users/c1587s/Dropbox/Webscrape_Puntajes/RawData/Basica2013.csv', header = FALSE, skip=1)
```

# 1.Open the browser and navigate the URL
#shell('docker run -d -p 4445:4444 selenium/standalone-firefox')
```{r}
remDr <- remoteDriver(remoteServerAddr = "localhost", port = 4445L, browserName = "firefox")
url_raw <- "http://143.137.111.105/Enlace/Resultados2013/Basica2013/R13Folio.aspx"
remDr$open(silent = TRUE) #opens a browser
remDr$navigate(url_raw) # Navigate the page with the browser
remDr$screenshot(display = TRUE)
#remDr$maxWindowSize()
```

Generating a test list - initial loop for the final script
```{r}
# for (folio in rawData_2010){ ...complete process } # after each loop a randow pause
Rowcount <- 1
folio_test <- rawData_2013[1]
```

# 2. Fill in the form to make the query with FOLIO keys
```{r}
folio <- as.character(folio_test)
searchID<-'//*[(@id = "txtFolioAlumno")]' # form to fill in with the folio number
webElem<-remDr$findElement(using = 'xpath', value = searchID) # find the form
webElem$sendKeysToElement(list(folio)) # fill in the form with the folio number
ConsButton <- '//*[(@id = "btnConsulta")]' # xpath to the "consultar" button
webElem <- remDr$findElement(value = ConsButton) # find the button
webElem$clickElement() # click on it
Sys.sleep(1)
remDr$screenshot(display = TRUE)
```

# 3. Generating the dataframe
```{r}
pregs_gral_names <-  c("Folio", "Grado", "Grupo", "Turno", "TipoDeEscuela", "NombreDeLaEscuela", "CCT", "Entidad", "GradoDeMarginacion", "PuntajeTotalEsp", "PuntajeTotalMat")
# List of names for Español questions
Mat_correcta <- c(); Mat_marcada <- c(); Esp_correcta <- c(); Esp_marcada <- c()
for (i in seq(1, 130, by=1)) {
  Mat_correcta[[i]] <- paste("MatCorrecta", as.character(i), sep="_")
  Mat_marcada[[i]] <- paste("MatMarcada", as.character(i), sep="_")
  Esp_correcta[[i]] <- paste("EspCorrecta", as.character(i), sep="_")
  Esp_marcada[[i]] <- paste("EspMarcada", as.character(i), sep="_")
}
dataBase_names <- c(pregs_gral_names, Esp_correcta, Esp_marcada, Mat_correcta, Mat_marcada)
DataBase = data.frame(matrix(ncol=531,nrow=1))
colnames(DataBase) <- dataBase_names
DataBase <- data.frame(lapply(DataBase, as.character), stringsAsFactors=FALSE)
Sys.sleep(1)
```


# 4. Extract general information
```{r}
tableID <- '/html/body/form/div[4]/center/div[1]/div[2]/div/div/table' # xpath to the general information table
webElemTable <- remDr$findElement(using = 'xpath', value = tableID) # get into the table
GeneralTable_parsed <- htmlParse(remDr$getPageSource()[[1]]) # extract the parsed html table
GeneralTable <- readHTMLTable(GeneralTable_parsed)
GeneralTable <- GeneralTable[[2]] # 2 is the number of the df with the desired info
#GeneralTable
col1Values <- GeneralTable$V3
col2Values <- GeneralTable$V5

DataBase$Folio[[Rowcount]] <- (levels(col1Values)[1])
DataBase$Grado[[Rowcount]] <- (levels(col1Values)[6])
DataBase$Grupo[[Rowcount]] <- (levels(col1Values)[2])
DataBase$Turno[[Rowcount]] <- (levels(col1Values)[5])
DataBase$TipoDeEscuela[[Rowcount]] <- (levels(col1Values)[3])
DataBase$NombreDeLaEscuela[[Rowcount]] <- (levels(col1Values)[4])
DataBase$CCT[[Rowcount]] <- as.character(levels(col2Values)[1])
DataBase$Entidad[[Rowcount]] <- as.character(levels(col2Values)[2])
DataBase$GradoDeMarginacion[[Rowcount]]<- as.character(levels(col2Values)[3])
```

# 5. General results for: español and matemáticas
```{r}
FrameID <- '//*[(@id = "idframe1")]'
webFrames <- remDr$findElements(using = 'xpath', value = FrameID)
sapply(webFrames, function(x){x$getElementAttribute("src")})
remDr$switchToFrame(webFrames[[1]])
# Resultados de español
res_esp <- '//*[@id="lblAsig1"]'
ResultEspElem <- remDr$findElement(using = 'xpath', value = res_esp ) # get into the table
ResultEsp <- ResultEspElem$getElementText()
# Resultados de matemáticas
res_mat <- '//*[@id="lblAsig2"]'
ResultMatElem <- remDr$findElement(using = 'xpath', value = res_mat) # get into the table
ResultMat <- ResultMatElem$getElementText()
DataBase$PuntajeTotalEsp[[Rowcount]] <- as.integer(ResultEsp)
DataBase$PuntajeTotalMat[[Rowcount]] <- as.integer(ResultMat)
# Exiting the frame
remDr$switchToFrame(NULL)
remDr$screenshot(display = TRUE)
```

# 6.  Respuesta de mi hija(o) en Español
  elemento_preg <- remDr$findElement(value = preguntaID)
  remDr$executeScript("arguments[0].click();", list(elemento_preg))

```{r}
CalifEspanolButton <- '//*[@id="__tab_TabContainer1_TabPanel2"]'
webElem <- remDr$findElement(value = CalifEspanolButton)
remDr$executeScript("arguments[0].click();", list(webElem))
FrameEspID <- '//*[(@id = "idframe2")]'
webFramesEsp <- remDr$findElements(using = 'xpath', value = FrameEspID)
sapply(webFramesEsp, function(x){x$getElementAttribute("src")})
remDr$switchToFrame(webFramesEsp[[1]])
remDr$screenshot(display = TRUE)
```

4.1 SECTIONS
```{r}
# List of names for Español questions
## T1: Aspectos sintácticos y semánticos
Esp_first_col_T1  <- c()
## T2: Búsqueda y manejo de la información
Esp_first_col_T2 <- c()
## T3: Comprensión e interpretación
Esp_first_col_T3 <- c(); Esp_second_col_T3 <- c(); Esp_third_col_T3 <- c()
## T4: Conocimiento del sistema de escritura y ortografía
Esp_first_col_T4 <- c()
# T5: Propiedades y características de los textos
Esp_first_col_T5 <- c(); Esp_second_col_T5 <- c()

for (i in seq(1,10, by=1)){
  Esp_first_col_T3[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[9]/td[2]/table/tbody/tr[1]/td[",
                          as.character(i), "]/a", sep="")
  Esp_second_col_T3[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[9]/td[2]/table/tbody/tr[2]/td[",
                          as.character(i), "]/a", sep="")
  Esp_first_col_T5[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[13]/td[2]/table/tbody/tr[1]/td[",
                          as.character(i), "]/a", sep="")
}
for (i in seq(1,8, by=1)){
  Esp_first_col_T1[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[5]/td[2]/table/tbody/tr/td[",
                          as.character(i), "]/a", sep="")
}
for (i in seq(1,5, by=1)){
  Esp_second_col_T5[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[13]/td[2]/table/tbody/tr[2]/td[",
                          as.character(i), "]/a", sep="")

}

for (i in seq(1,4, by=1)){
  Esp_first_col_T4[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[11]/td[2]/table/tbody/tr/td[",
                          as.character(i), "]/a", sep="")
}
for (i in seq(1,3, by=1)){
  Esp_first_col_T2[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[7]/td[2]/table/tbody/tr/td[",
                          as.character(i), "]/a", sep="")
}
for (i in seq(1,2, by=1)){
  Esp_third_col_T3[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[9]/td[2]/table/tbody/tr[3]/td[",
                          as.character(i), "]/a", sep="")
}


# paste all the elements
Esp_T1 <- c(Esp_first_col_T1)
Esp_T2 <- c(Esp_first_col_T2)
Esp_T3 <- c(Esp_first_col_T3,Esp_second_col_T3, Esp_third_col_T3)
Esp_T4 <- c(Esp_first_col_T4)
Esp_T5 <- c(Esp_first_col_T5, Esp_second_col_T5)

pregs_esp <- c(Esp_T1,Esp_T2,Esp_T3,Esp_T4,Esp_T5)
```

## 6.1 Exctract the information
```{r}
  for (i in seq(1,length(pregs_esp), by=1)){
  preguntaID<- pregs_esp[[i]]

  nroPreguntaID <- paste(preguntaID, "/font/strong", sep ="")
  nroPreguntaElem <- remDr$findElement(value = nroPreguntaID)
  nroPregunta <- nroPreguntaElem$getElementText()
  nroPregunta_i <- gsub("(?<![0-9])0+", "", nroPregunta, perl = TRUE) # for omitting leading zeroes
  nroPregunta_int <- as.integer(nroPregunta_i)
  print(nroPregunta_int)
  # Now, click on each question
  elemento_preg <- remDr$findElement(value = preguntaID)
  remDr$executeScript("arguments[0].click();", list(elemento_preg))
  Sys.sleep(1.2) # This part is mandatory, we need to include a pause to load the data correctly
  preg_correctaID <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[2]/tbody/tr[1]/td/b")
  correctaInfo    <- preg_correctaID$getElementText()
  preg_marcadaID  <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[2]/tbody/tr[2]/td/b")
  marcadaInfo     <- preg_marcadaID$getElementText()
  # Asign values to the database using the question number
  DataBase[folioID, nroPregunta_int+11] <-as.character(correctaInfo) # Esp correcta (+11 is the correction to math the position in the DF)
  DataBase[folioID, nroPregunta_int+141] <-as.character(marcadaInfo)# Esp marcada (+131 is the correction to math the position in the DF)

  # going back to the frame
  regTablero <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[3]/tbody/tr/td/span")
  remDr$executeScript("arguments[0].click();", list(regTablero))
  Sys.sleep(1.2)

}
# Exiting the frame
remDr$switchToFrame(NULL)
```


# 7 Respuesta de mi hija(o) en Matemáticas

```{r}
CalifMatematicasButton <- '//*[@id="__tab_TabContainer1_TabPanel3"]'
webElem <- remDr$findElement(value = CalifMatematicasButton)
remDr$executeScript("arguments[0].click();", list(webElem))
FrameEspID <- '//*[(@id = "idframe3")]'
webFramesEsp <- remDr$findElements(using = 'xpath', value = FrameEspID)
sapply(webFramesEsp, function(x){x$getElementAttribute("src")})
remDr$switchToFrame(webFramesEsp[[1]])
remDr$screenshot(display = TRUE)

# List of names for Matematicas questions
## T1: Medida
Mat_first_col_T1  <- c()
## T2: Números y sistemas de numeración
Mat_first_col_T2 <- c(); Mat_second_col_T2 <- c()
## T3: Problemas aditivos
Mat_first_col_T3 <- c()
## T4: Problemas multiplicativos
Mat_first_col_T4 <- c(); Mat_second_col_T4 <- c(); Mat_third_col_T4 <- c()

for (i in seq(1,10, by=1)){
  Mat_first_col_T2[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[7]/td[2]/table/tbody/tr[1]/td[",
                          as.character(i), "]/a", sep="")
  Mat_first_col_T4[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[11]/td[2]/table/tbody/tr[1]/td[",
                          as.character(i), "]/a", sep="")
  Mat_second_col_T4[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[11]/td[2]/table/tbody/tr[2]/td[",
                          as.character(i), "]/a", sep="")
}
for (i in seq(1,5, by=1)){
  Mat_second_col_T2[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[7]/td[2]/table/tbody/tr[2]/td[",
                          as.character(i), "]/a", sep="")
}
for (i in seq(1,3, by=1)){
  Mat_first_col_T1[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[5]/td[2]/table/tbody/tr/td[",
                          as.character(i), "]/a", sep="")
}
for (i in seq(1,2, by=1)){
  Mat_first_col_T3[[i]] <- paste("/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[9]/td[2]/table/tbody/tr/td[",
                          as.character(i), "]/a", sep="")
}

Mat_third_col_T4[[1]] <- "/html/body/form/div[3]/div/table/tbody/tr[7]/td/table[1]/tbody/tr[11]/td[2]/table/tbody/tr[3]/td/a"

# paste all the elements
Mat_T1 <- c(Mat_first_col_T1)
Mat_T2 <- c(Mat_first_col_T2, Mat_second_col_T2)
Mat_T3 <- c(Mat_first_col_T3)
Mat_T4 <- c(Mat_first_col_T4, Mat_second_col_T4, Mat_third_col_T4)

preguntas_mat <- c(Mat_T1,Mat_T2,Mat_T3,Mat_T4)
remDr$screenshot(display = TRUE)
```


## 7.1 Extract the information
```{r}
  for (i in seq(1,length(preguntas_mat), by=1)){
  preguntaID<- preguntas_mat[[i]]

  nroPreguntaID <- paste(preguntaID, "/font/strong", sep ="")
  nroPreguntaElem <- remDr$findElement(value = nroPreguntaID)
  nroPregunta <- nroPreguntaElem$getElementText()
  nroPregunta_i <- gsub("(?<![0-9])0+", "", nroPregunta, perl = TRUE) # for omitting leading zeroes
  nroPregunta_int <- as.integer(nroPregunta_i)
  print(nroPregunta_int)
  # Now, click on each question
  elemento_preg <- remDr$findElement(value = preguntaID)
  remDr$executeScript("arguments[0].click();", list(elemento_preg))
  Sys.sleep(1.2) # This part is mandatory, we need to include a pause to load the data correctly
  preg_correctaID <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[2]/tbody/tr[1]/td/b")
  correctaInfo    <- preg_correctaID$getElementText()
  preg_marcadaID  <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[2]/tbody/tr[2]/td/b")
  marcadaInfo     <- preg_marcadaID$getElementText()
  # Asign values to the database using the question number
  DataBase[Rowcount, nroPregunta_int+271] <-as.character(correctaInfo) # Mat correcta (+251 is the correction to math the position in the DF)
  DataBase[Rowcount, nroPregunta_int+401] <-as.character(marcadaInfo) # Mat marcada (+371 is the correction to math the position in the DF)

  # going back to the frame
  regTablero <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[3]/tbody/tr/td/span")
  remDr$executeScript("arguments[0].click();", list(regTablero))
  Sys.sleep(1.2)

  }
# Exiting the frame
remDr$switchToFrame(NULL)
```

## 7.1 Extract the information
```{r}
  for (i in seq(1,length(preguntas_mat), by=1)){
  preguntaID<- preguntas_mat[[i]]

  nroPreguntaID <- paste(preguntaID, "/font/strong", sep ="")
  nroPreguntaElem <- remDr$findElement(value = nroPreguntaID)
  nroPregunta <- nroPreguntaElem$getElementText()
  nroPregunta_i <- gsub("(?<![0-9])0+", "", nroPregunta, perl = TRUE) # for omitting leading zeroes
  nroPregunta_int <- as.integer(nroPregunta_i)
  print(nroPregunta_int)
  # Now, click on each question
  elemento_preg <- remDr$findElement(value = preguntaID)
  remDr$executeScript("arguments[0].click();", list(elemento_preg))
  Sys.sleep(1.2) # This part is mandatory, we need to include a pause to load the data correctly
  preg_correctaID <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[2]/tbody/tr[1]/td/b")
  correctaInfo    <- preg_correctaID$getElementText()
  preg_marcadaID  <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[2]/tbody/tr[2]/td/b")
  marcadaInfo     <- preg_marcadaID$getElementText()
  # Asign values to the database using the question number
  DataBase[Rowcount, nroPregunta_int+251] <-as.character(correctaInfo) # Mat correcta (+251 is the correction to math the position in the DF)
  DataBase[Rowcount, nroPregunta_int+371] <-as.character(marcadaInfo)# Esp marcada (+371 is the correction to math the position in the DF)

  # going back to the frame
  regTablero <- remDr$findElement(value = "/html/body/form/div[3]/div/table/tbody/tr[5]/td/table[3]/tbody/tr/td/span")
  remDr$executeScript("arguments[0].click();", list(regTablero))
  Sys.sleep(1.2)

  }
# Exiting the frame
remDr$switchToFrame(NULL)
```

# Random pause before next query - add one to the counter
```{r}
random_num <- runif(1,1,5)
Sys.sleep(random_num)

Rowcount <- Rowcount + 1
```

### After the loop finishes, write a CSV file

```{r}
write.csv(DataBase, file="/Users/c1587s/Dropbox/Webscrape_Puntajes/CreatedData/2013/DataBase_ENLACE2013_Test.csv", row.names = FALSE)
# Append = TRUE is a good option to append if we want to run the code by chunks of data
```

# Send an e-mail when the process is finished
```{r}
from <- "<s.cadavid1587@gmail.com>"
to <- "<s.cadavid1587@gmail.com>"
subject <- "R scraping for ENLACE 2013"
body <- "R scraping for ENLACE 2013 is has stopped for a reason."
mailControl=list(smtpServer="snmpt server address")
sendmail(from=from,to=to,subject=subject,msg=body,control=mailControl)
```
